Towards the Development of an Intelligent Building Energy Management System -- iBEMS \thanks{The results presented in this paper were produced by a group of senior undergraduate students: Brian Lauer and Elliot Watkins }

### 2021-09-18 paperIEEE-IECON2021.tex
Moved architecture paragraph to implementation, added note about scalability

At the center of the iBEMS architecture is the iBEMS core. This core interacts
with multiple peripherals including IoT devices and a weather API over the
internet. In this work, we developed the iBEMS to support for two 
IoT devices displayed in the high-level architecture shown in Fig.~\ref{fig:highLevelArchitecture}. %
%
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.15]{figs/overallConnectionDiagram.pdf}
  \caption{High-level architecture of the proposed iBEMS.}
  \label{fig:highLevelArchitecture}
\end{figure}
%
These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone
Blue.  The core is also able to
connect the internet to download weather data for a local city through
OpenWeatherMap. Fig.~\ref{fig:functional_bd} gives the lower level functional block diagram of the system
architecture. %
%
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.3]{figs/functionalBlockDiagram.pdf}
  \caption{Functional Block Diagram}
  \label{fig:functional_bd}
\end{figure}
%
The inputs include the user input through the web server, the device status
updates (On/Off, power usage, etc...) and the weather data. The iBEMS Core
itself consists of a Flask Web Server, 2 databases (Apache Cassandra and
SQLite), and 3 software agents (Discovery, Control, and Scheduling).

The Flask web server is built using a Python web framework titled Flask which
allows programmers to develop a dynamic web server capable of rendering data to
HTML pages. The benefit of this framework over other Python web frameworks like
Django is the large amount of customization available. For example, the
developers can create a completely custom user login system. For now, the server
is capable of being accessed only on the server computer running Ubuntu Linux.
In the future, support could be added to allow any user on the LAN to access the
web server. Other web frameworks use object relational mapping directly to
access the relevant databases. However, the current iBEMS uses direct queries with both
SQLite and the Cassandra query language to query the databases. We used
2 different databases to store information on. The Apache Cassandra database was
better suited for the time series data such as device status and power usage.
This database was therefore utilized a lot by the Control and Scheduling Agents.
The SQLite database hold parameters that do not change over time like device
ID's, IP addresses, and MAC addresses which made it amendable to the processes
in the Discovery Agent. The first agent that is
used by the iBEMS Core on startup is the discovery agent. It is responsible for
reaching out on the network and finding all devices that the iBEMS Core has
support for. This process involves retrieving the following parameters: IP
address, Port number, MAC address, Manufacturer, Name, and API. Once all
available devices are connected, the Control agent is used to change the status
of each device and collect power usage data in real time. Finally, the
scheduling will take input from the user and place the corresponding scheduling
periods in the Apache Cassandra database. Then, a thread is created to poll the
current device status at regular intervals and update the status if it does not
match the defined status in the Apache Cassandra database.

@@

\section{Software Implementation}
\label{sec:SoftwareImplementation}

@@

One of the main ways to improve the software is to refactor the user interface as the current interface is fairly primitive. Adding elements like collapsible drop down menus and a collapsible side bar would make the interface more professional and user-friendly. To improve the overall reliability and speed of the software, a better agent communication protocol could be researched and implemented. Many problems are visible with the use of ZeroMQ as exceptions are thrown occasionally when device status updates are sent in quick succession to the control agent. Potentially, there exists a better solution than publish-subscribe. One of the major issues with the software is lack of device data persistence across system restarts. Developers in the future could help alleviate this problem by refactoring the device storage system in the Cassandra database.

>>>>

At the center of the iBEMS architecture is the iBEMS core. This core interacts
with multiple peripherals including IoT devices and a weather API over the
internet. In this work, we developed the iBEMS to support two IoT devices displayed in the high-level architecture shown in Fig.~\ref{fig:highLevelArchitecture}. %
%
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.15]{figs/overallConnectionDiagram.pdf}
  \caption{High-level architecture of the proposed iBEMS.}
  \label{fig:highLevelArchitecture}
\end{figure}
%
These devices are the WeMo Insight Switch and an embedded computer known as the Beaglebone
Blue.  The core is also able to
connect to the internet to download weather data for a local city through
OpenWeatherMap. Fig.~\ref{fig:functional_bd} gives the lower level functional block diagram of the system
architecture. %
%
\begin{figure}[htbp]
  \centering
  \includegraphics[scale=0.3]{figs/functionalBlockDiagram.pdf}
  \caption{Functional Block Diagram}
  \label{fig:functional_bd}
\end{figure}
%
The inputs include the user input through the web server, the device status
updates (On/Off, power usage, etc...) and the weather data. The iBEMS Core
itself consists of a Flask Web Server, 2 databases (Apache Cassandra and
SQLite), and 3 software agents (Discovery, Control, and Scheduling).

@@

\section{Software Implementation}
\label{sec:SoftwareImplementation}
The Flask web server is built using a Python web framework titled Flask which
allows programmers to develop a dynamic web server capable of rendering data to
HTML pages. The benefit of this framework over other Python web frameworks like
Django is the large amount of customization available. For example, the
developers can create a completely custom user login system. For now, the server
is capable of being accessed only on the server computer running Ubuntu Linux.
In the future, support could be added to allow any user on the LAN to access the
web server. Other web frameworks use object relational mapping directly to
access the relevant databases. However, the current iBEMS uses direct queries with both
SQLite and the Cassandra query language to query the databases. We used
2 different databases to store information on. The Apache Cassandra database was
better suited for the time series data such as device status and power usage.
This database was therefore utilized a lot by the Control and Scheduling Agents.
The SQLite database hold parameters that do not change over time like device
ID's, IP addresses, and MAC addresses which made it amendable to the processes
in the Discovery Agent. The first agent that is
used by the iBEMS Core on startup is the discovery agent. It is responsible for
reaching out on the network and finding all devices that the iBEMS Core has
support for. This process involves retrieving the following parameters: IP
address, Port number, MAC address, Manufacturer, Name, and API. Once all
available devices are connected, the Control agent is used to change the status
of each device and collect power usage data in real time. Finally, the
scheduling will take input from the user and place the corresponding scheduling
periods in the Apache Cassandra database. Then, a thread is created to poll the
current device status at regular intervals and update the status if it does not
match the defined status in the Apache Cassandra database.

@@

One of the main ways to improve the software is to refactor the user interface as the current interface is fairly primitive. Adding elements like collapsible drop down menus and a collapsible side bar would make the interface more professional and user-friendly. To improve the overall reliability and speed of the software, a better agent communication protocol could be researched and implemented. Many problems are visible with the use of ZeroMQ as exceptions are thrown occasionally when device status updates are sent in quick succession to the control agent. Scalability is another issue that comes to mind as users will undoubtedly want to connect more than two devices. Potentially, there exists a better solution than publish-subscribe. One of the major issues with the software is lack of device data persistence across system restarts. Developers in the future could help alleviate this problem by refactoring the device storage system in the Cassandra database.
